---
title: "4. Generating model summaries"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{4. Generating model summaries}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
options(rmarkdown.html_vignette.check_title = FALSE)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE, 
  message = FALSE
)
```

```{r setup}
library(quollr)
library(dplyr)
library(ggplot2)
```

To obtain the model summaries, first you need to obtain the 2D hexagonal bin centroids which is the 2D model (`df_bin_centroids`) and the high-dimensional coordinates of bin centroids which represents the lifted model in high-dimensions (`df_bin`).

```{r}
r2 <- diff(range(s_curve_noise_umap$UMAP2))/diff(range(s_curve_noise_umap$UMAP1))
model <- fit_highd_model(training_data = s_curve_noise_training, 
                         emb_df = s_curve_noise_umap_scaled,
                         bin1 = 6, r2 = r2,
                         col_start_highd = "x")
df_bin_centroids <- model$df_bin_centroids
df_bin <- model$df_bin
```

Let's first compute the model summaries for training data. To do that, you need to predict 2D embedding for the training data.

```{r}
pred_df_training <- predict_emb(test_data = s_curve_noise_training, 
                             df_bin_centroids = df_bin_centroids, 
                             df_bin = df_bin, type_NLDR = "UMAP")
glimpse(pred_df_training)
```

```{r}
s_curve_noise_umap_scaled |>
    ggplot(aes(x = UMAP1,
               y = UMAP2,
               label = ID))+
    geom_point(alpha=0.5) +
    geom_point(data = pred_df_training, aes(x = pred_UMAP_1, y = pred_UMAP_2), 
               color = "red", alpha=0.5) +
    coord_equal() +
    theme(plot.title = element_text(hjust = 0.5, size = 18, face = "bold"),
          axis.text = element_text(size = 5),
          axis.title = element_text(size = 7))
```

Next, you can use the generated 2D embedding to compute model summaries.

```{r}
glance(df_bin_centroids = df_bin_centroids, df_bin = df_bin, 
        training_data = s_curve_noise_training, newdata = NULL, 
        type_NLDR = "UMAP", col_start = "x")
```

To obtain a dataframe with the high-dimensional data, the fitted model data, the predicted NLDR data, and summary information, you can use the following function.

```{r}
augment(df_bin_centroids = df_bin_centroids, df_bin = df_bin, 
        training_data = s_curve_noise_training, newdata = NULL, 
        type_NLDR = "UMAP", col_start = "x") |>
  head(5)
```

The same workflow is followed for the test data as well.

```{r}
pred_df_test <- predict_emb(test_data = s_curve_noise_test, 
                             df_bin_centroids = df_bin_centroids, 
                             df_bin = df_bin, type_NLDR = "UMAP")
```

```{r}
s_curve_noise_umap_scaled |>
    ggplot(aes(x = UMAP1,
               y = UMAP2,
               label = ID))+
    geom_point(alpha=0.5) +
    geom_point(data = pred_df_test, aes(x = pred_UMAP_1, y = pred_UMAP_2), 
               color = "red", alpha=0.5) +
    coord_equal() +
    theme(plot.title = element_text(hjust = 0.5, size = 18, face = "bold"),
          axis.text = element_text(size = 5),
          axis.title = element_text(size = 7))
```

```{r}
glance(df_bin_centroids = df_bin_centroids, df_bin = df_bin, 
        training_data = s_curve_noise_training, newdata = s_curve_noise_test, 
        type_NLDR = "UMAP", col_start = "x")
```

```{r}
augment(df_bin_centroids = df_bin_centroids, df_bin = df_bin, 
        training_data = s_curve_noise_training, newdata = s_curve_noise_test, 
        type_NLDR = "UMAP", col_start = "x") |>
  head(5)
```
