---
title: "3. Algorithm for visualising the model overlaid on high-dimensional data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{3. Algorithm for visualising the model overlaid on high-dimensional data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
options(rmarkdown.html_vignette.check_title = FALSE)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE, 
  message = FALSE
)
```

In here, we'll walk through the algorithm for preprocessing 2D embedding data to construct a model overlaid with high-dimensional data.

```{r setup}
library(quollr)
library(ggplot2)
library(tibble)
library(dplyr)
library(stats)
```

The algorithm consists of two steps. First, construct the model in 2D space. Second, lift the model into high-dimensions. Therefore, to begin the process, first you need to know how the 2D model is constructed.

## Construct the 2D model

### Binning the data

To construct the model in the 2D space, first you need to hexagonally bins the 2D layout. Discussed in details in [3. Algorithm for binning data](https://quollr.netlify.app/articles/visfullgrid).  

```{r}
lim1 <- s_curve_obj$s_curve_umap_scaled_obj$lim1
lim2 <- s_curve_obj$s_curve_umap_scaled_obj$lim2
r2 <- diff(lim2)/diff(lim1)

umap_scaled <- s_curve_obj$s_curve_umap_scaled_obj$scaled_nldr

hb_obj <- hex_binning(data = umap_scaled, bin1 = 15, r2 = r2)

all_centroids_df <- hb_obj$centroids
counts_df <- hb_obj$std_cts
```

### Obtain bin centroids

Nest step is to obtain the hexagonal bin centroid coordinates (`all_centroids_df`) and standard number of points within each hexagon (`counts_df`). Then, you can generate tibble which gives hexagonal ID, centroid coordinates and standard counts where data exists.

```{r}
df_bin_centroids <- extract_hexbin_centroids(centroids_df = all_centroids_df,
                                             counts_df = counts_df) 

glimpse(df_bin_centroids) 
```

### Triangulate bin centroids

Then, you need to triangulate the bin centroids.

```{r}
tr1_object <- tri_bin_centroids(hex_df = df_bin_centroids, x = "c_x", y = "c_y")
str(tr1_object)
```

To visualize the results, simply use `geom_trimesh()` and provide the hexagonal bin centroid coordinates. This will display the triangular mesh for you to examine.

```{r, fig.alt="Triangular mesh."}
trimesh <- ggplot(df_bin_centroids, aes(x = c_x, y = c_y)) +
  geom_trimesh() +
  coord_equal() +
  xlab(expression(C[x]^{(2)})) + ylab(expression(C[y]^{(2)})) +
  theme(axis.text = element_text(size = 5),
        axis.title = element_text(size = 7))

trimesh
```

### Create the wireframe in 2D

To build the wireframe in 2D, you'll need to identify which vertices are connected. You can obtain this by passing the triangular object to the `gen_edges` function, which will provide information on the existing edges and the connected vertices.

```{r}
tr_from_to_df <- gen_edges(tri_object = tr1_object, threshold = 0)
glimpse(tr_from_to_df)
```


To visualize the results, you can use `vis_rmlg_mesh()`. This function enable you to observe the wireframe in 2D obtained from the algorithm's computations.

```{r, fig.alt="Triangular mesh after removing low-density hexagons."}
trimesh_removed <- vis_rmlg_mesh(tr_coord_df = tr_from_to_df) +
  xlab(expression(C[x]^{(2)})) + ylab(expression(C[y]^{(2)})) +
  theme(axis.text = element_text(size = 5),
        axis.title = element_text(size = 7))

trimesh_removed
```

## Lift the model into high-dimensions

To lift the constructed model into high-dimensions, you need to map the 2D hexagonal bin centroids to high-dimensions. To do that, first, you need to obtain the data set which have the 2D embedding with their corresponding hexagonal bin IDs.

```{r}
umap_data_with_hb_id <- hb_obj$data_hb_id
glimpse(umap_data_with_hb_id)
```

Next, you need to create a data set with the high-dimensional data and the 2D embedding with hexagonal bin IDs.

```{r}        
df_all <- dplyr::bind_cols(s_curve_noise_training |> dplyr::select(-ID), umap_data_with_hb_id)
glimpse(df_all)
```

Then, use `avg_highd_data()` to obtain the high-dimensional coordinates of the model.

```{r} 
df_bin <- avg_highd_data(data = df_all)
glimpse(df_bin)
```

## Result

Finally, to visualise the model overlaid with the high-dimensional data, you initially need to pass the data set with the high-dimensional data and the 2D embedding with hexagonal bin IDs (`df_all`),  high-dimensional mapping of hexagonal bin centroids (`df_bin`), 2D hexagonal bin coordinates (`df_bin_centroids`), and wireframe data (`distance_df`).

```{r}
df_bin_centroids <- df_bin_centroids |>
  dplyr::filter(std_counts > 0)

df_exe <- comb_data_model(highd_data = s_curve_noise_training, model_highd = df_bin, model_2d = df_bin_centroids)
```

```{r}
tour1 <- show_langevitour(point_df = df_exe, edge_df = tr_from_to_df)

tour1
```
