---
title: "quollr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{quollr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(quollr)
library(ggplot2)
```

quollr constructs low-dimensional manifolds by combining Non-Linear Dimension Reduction (NLDR), hexagonal binning, and triangulation techniques, enabling accurate high-dimensional data representations. The package integrates these manifolds with original data using the tour technique, while also offering tools for generating simulated data sets for comprehensive exploration.

To start with quollr, refer to the package documentation and explore its functions

<!--An associated paper can be found at-->

## Installation

You can install the development version of quollr from GitHub with:

```{r}
#install.packages("remotes")
#remotes::install_github("JayaniLakshika/quollr")
```

## Usage

The package's functionalities as follows:

To begin, you need to load the high-dimensional data and 2D embeddings.

```{r}
training_data <- readr::read_rds(file = paste0(here::here(), "/data/s_curve_noise_training.rds"))
UMAP_data <- readr::read_rds(file = paste0(here::here(), "/data/s_curve_noise_umap.rds"))
```

1. **Optimize Hexagonal Grid**: Determine the optimal hexagonal grid configuration by calculating the number of bins and shape parameter using `calculate_effective_x_bins()` and `calculate_effective_shape_value()`.

```{r}
num_bins_x <- calculate_effective_x_bins(.data = UMAP_data, x = UMAP1,
                           cell_area = 1)

shape_val <- calculate_effective_shape_value(.data = UMAP_data, 
                                             x = UMAP1, y = UMAP2)
```

2. **Generate Hexagonal Object**: Use the calculated parameters to generate a hexagonal object, representing the spatial distribution of data points.

```{r}
hb_object <- hexbin::hexbin(x = UMAP_data |> dplyr::pull(UMAP1), 
                     y = UMAP_data |> dplyr::pull(UMAP2), 
                     xbins = num_bins_x, IDs = TRUE, 
                     shape = shape_val)
```

3. **Create Hex Bin Plot**: Visualize the hex bin plot to observe data density within each hex bin.

4. **Assign Data Observations to Hex Bins**: Assign high-dimensional data points to corresponding hex bins using the `create_hexbin()` function.

```{r}
hexbin <- create_hexbin(.data = training_data, nldr_df = UMAP_data, 
                        embedding_1 = UMAP1, embedding_2 = UMAP2, 
                        num_bins = num_bins_x, shape_val = shape_val, 
                        apply_pca = FALSE)

df_all <- hexbin$df
hb_object <- hexbin$hb
```

5. **Compute High-Dimensional Average**: Compute the average of high-dimensional data for each hex bin.

```{r}
df_bin <- avg_highD_data(.data = df_all, apply_pca = FALSE)
```

6. **Extract Bin Centroids**: Extract bin centroids for further processing.

```{r}
df_bin_centroids <- extract_hexbin_centroids(.data = df_bin, hb = hb_object)
```

7. **Address Low-Density Hexagons**: Filter out low-density hexagons to enhance data representation.

```{r}
min_std_cell_threshold <- 0.05
df_bin_centroids <- df_bin_centroids |>
  dplyr::mutate(stand_cell_count = Cell_count/max(Cell_count)) |>
  dplyr::filter(stand_cell_count > min_std_cell_threshold)
```

8. **Triangulate Bin Centroids**: Triangulate the centroids of hex bins.

```{r}
tr1_object <- triangulate_bin_centroids(df_bin_centroids)
```

9. **Generate Edge Information**: Create a dataset containing edge information for each triangle.

```{r}
tr_from_to_df <- generate_edge_info(triangular_object = tr1_object)
```

10. **Calculate 2D Distances**: Calculate 2D distances between edges.

```{r}
distance <- cal_2D_dist(.data = tr_from_to_df)
```

11. **Visualize Triangulated Mesh**: Visualize the triangulated mesh in low-dimensional space.

```{r}
trimesh <- ggplot(df_bin_centroids, aes(x = x_val_center, y = y_val_center)) + 
  geom_point(size = 0.1) + 
  geom_trimesh() + 
  coord_equal() 

trimesh
```

12. **Remove Long Edges**: Enhance the representation by removing long edges.

```{r}
benchmark <- find_benchmark_value(.data = distance, distance_col = distance)
trimesh_gr <- colour_long_edges(.data = distance, benchmark_value = benchmark, 
                 triangular_object = tr1_object, distance_col = distance) 

trimesh_gr
```

13. **Tour View**: Visualize the tour that simultaneously displays the original and model data along with the learned low-dimensional manifold in high-dimensional space.

```{r}
show_langevitour(df_all, df_bin, df_bin_centroids, benchmark_value = benchmark, distance, distance)
```

By following these steps, you can effectively leverage **quollr** to construct informative low-dimensional representations of high-dimensional data, while also benefitting from its simulated data generation functions to explore various scenarios and conditions.


## Copyright

This package is licensed under the [MIT license](https://github.com/JayaniLakshika/quollr/LICENSE.md). 
